Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-03 mr-review.Rmd
reorganized a paragraph

Now, GWAS and Mendelian randomization for biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller sample sizes.

@@

## Statistical models for MR with one instrument and one outcome

## Statistical methods for MR with one instrument and one outcome

>>>>

Now, GWAS and Mendelian randomization for biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies, often greater than 100,000 subjects, offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller studies.

@@

## Statistical models and methods for MR with one instrument and one outcome
